Timeliness of security updates for Android

### 2014-11-12 avostats.tex
Updated graphs and avo data
updated data and some figures

\newcommand{\avoNumSubmitters}{7}
\newcommand{\avoTotalExternalLines}{25 Million}
\newcommand{\avoNumExternalProjects}{176}
\newcommand{\avoNumBigExternalLinesOfCode}{25 Million}
\newcommand{\avoBigExternalLinesOfCodePerc}{99.69\%}
\newcommand{\avoNumVulnerabilities}{31}
\newcommand{\avoNumVulnAllAndroid}{15}
\newcommand{\avoNumVulnSpecific}{16}
\newcommand{\avoStartDate}{2013-08-28}
\newcommand{\avoEndDate}{2014-10-17}
\newcommand{\avoFirstDataDate}{2010-07-13}
\newcommand{\avoLastDataDate}{2014-07-29}
\newcommand{\avoVulnsPerYearNominal}{7.66}
\newcommand{\avoVulnsPerYear}{$7.7 \pm 1.4$}
\newcommand{\avoVulnsPerYearAllAndroidNominal}{3.71}
\newcommand{\avoVulnsPerYearAllAndroid}{$3.7 \pm 1.0$}
\newcommand{\avoTabAndVulns}{\begin{table} \centering \begin{tabular}{l|l|c} Vulnerability & How known & Date \\ \hline KillingInTheNameOf psneuter ashmem & Fixed on & 2010-07-13 \\ exploid udev & Discovered on & 2010-07-15 \\ levitator & Discovered on & 2011-03-10 \\ Gingerbreak & Fixed on & 2011-04-18 \\ zergRush & Discovered on & 2011-10-06 \\ APK duplicate file & Discovered on & 2013-02-18 \\ APK unchecked name & Discovered on & 2013-06-30 \\ APK unsigned shorts & Fixed on & 2013-07-03 \\ vold asec & Fixed on & 2014-01-27 \\ Fake ID & Fixed on & 2014-04-17 \\ TowelRoot & Discovered on & 2014-05-03 \\\end{tabular} \caption{Root equivalent vulnerabilities in Android} \label{tab:andvulns} \end{table}}
\newcommand{\avoNumBigExternalProjects}{40}
\newcommand{\avoNumAnalysedExternalProjects}{28}
\newcommand{\avoNumAnalysedExternalLinesOfCode}{6 Million}
\newcommand{\avoAnalysedExternalLinesOfCodePerc}{24.85\%}
\newcommand{\avoBigExternalMedianVersions}{1.50}
\newcommand{\avoBigExternalMeanVersionsNominal}{2.07}
\newcommand{\avoBigExternalMeanVersions}{$2.1 \pm 1.4$}
\newcommand{\avoBigExternalTotalVersions}{58}

>>>>

\newcommand{\avoNumSubmitters}{7}
\newcommand{\avoTotalExternalLines}{25 Million}
\newcommand{\avoNumExternalProjects}{176}
\newcommand{\avoNumBigExternalLinesOfCode}{25 Million}
\newcommand{\avoBigExternalLinesOfCodePerc}{99.7\%}
\newcommand{\avoNumVulnerabilities}{31}
\newcommand{\avoNumVulnAllAndroid}{15}
\newcommand{\avoNumVulnSpecific}{16}
\newcommand{\avoStartDate}{2013-08-28}
\newcommand{\avoEndDate}{2014-10-17}
\newcommand{\avoFirstDataDate}{2010-07-13}
\newcommand{\avoLastDataDate}{2014-07-29}
\newcommand{\avoVulnsPerYearNominal}{7.66}
\newcommand{\avoVulnsPerYear}{$7.66 \pm 1.38$}
\newcommand{\avoVulnsPerYearAllAndroidNominal}{3.71}
\newcommand{\avoVulnsPerYearAllAndroid}{$3.71 \pm 0.957$}
\newcommand{\avoTabAndVulns}{\begin{table} \centering \begin{tabular}{l|l|c} Vulnerability & How known & Date \\ \hline KillingInTheNameOf psneuter ashmem & Fixed on & 2010-07-13 \\ exploid udev & Discovered on & 2010-07-15 \\ levitator & Discovered on & 2011-03-10 \\ Gingerbreak & Fixed on & 2011-04-18 \\ zergRush & Discovered on & 2011-10-06 \\ APK duplicate file & Discovered on & 2013-02-18 \\ APK unchecked name & Discovered on & 2013-06-30 \\ APK unsigned shorts & Fixed on & 2013-07-03 \\ vold asec & Fixed on & 2014-01-27 \\ Fake ID & Fixed on & 2014-04-17 \\ TowelRoot & Discovered on & 2014-05-03 \\\end{tabular} \caption{Critical vulnerabilities in Android} \label{tab:andvulns} \end{table}}
\newcommand{\avoNumBigExternalProjects}{40}
\newcommand{\avoNumAnalysedExternalProjects}{28}
\newcommand{\avoNumAnalysedExternalLinesOfCode}{6 Million}
\newcommand{\avoAnalysedExternalLinesOfCodePerc}{24.9\%}
\newcommand{\avoBigExternalMedianVersions}{1.5}
\newcommand{\avoBigExternalMeanVersionsNominal}{2.07}
\newcommand{\avoBigExternalMeanVersions}{$2.07 \pm 1.44$}
\newcommand{\avoBigExternalTotalVersions}{58}

### 2014-11-12 dastats.tex
updated data and some figures

\newcommand{\daMeanInsecurityPerc}{$87 \pm 0\%$}

@@

\newcommand{\daUpdatedness}{$0.056 \pm 0.000$}
\newcommand{\daSecurityScore}{$2.8 \pm 0.0$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline LG & $0.12 \pm 0.00$ & $0.32 \pm 0.00$ & 0.74 & $3.4 \pm 0.0$ \\  Motorola & $0.16 \pm 0.00$ & $0.13 \pm 0.00$ & 0.77 & $2.9 \pm 0.0$ \\  other & $0.13 \pm 0.00$ & $0.056 \pm 0.000$ & 0.64 & $2.8 \pm 0.0$ \\  Samsung & $0.14 \pm 0.00$ & $0.047 \pm 0.000$ & 0.71 & $2.7 \pm 0.0$ \\  Sony & $0.13 \pm 0.00$ & $0.18 \pm 0.00$ & 1.02 & $2.6 \pm 0.0$ \\  HTC & $0.14 \pm 0.00$ & $0.087 \pm 0.001$ & 0.89 & $2.6 \pm 0.0$ \\  asus & $0.16 \pm 0.00$ & $0.56 \pm 0.01$ & 6.06 & $2.3 \pm 0.0$ \\  Symphony & $0.0015 \pm 0.0002$ & $0.042 \pm 0.001$ & 4.87 & $0.18 \pm 0.00$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table}}
\newcommand{\daTabSecScoresmodel}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.54 \pm 0.00$ & $0.53 \pm 0.01$ & 1.53 & $4.8 \pm 0.0$ \\  Nexus 4 & $0.23 \pm 0.00$ & $0.82 \pm 0.01$ & 6.06 & $3.4 \pm 0.0$ \\  Nexus 7 & $0.19 \pm 0.00$ & $0.74 \pm 0.01$ & 5.92 & $3.0 \pm 0.0$ \\  other & $0.13 \pm 0.00$ & $0.12 \pm 0.00$ & 0.64 & $2.9 \pm 0.0$ \\  Desire HD & $0.083 \pm 0.003$ & $0.051 \pm 0.004$ & 0.39 & $2.9 \pm 0.0$ \\  HTC Sensation & $0.36 \pm 0.00$ & $0.0063 \pm 0.0062$ & 1.59 & $2.5 \pm 0.0$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.016 \pm 0.001$ & 1.20 & $2.3 \pm 0.0$ \\  HTC Desire S & $0.022 \pm 0.001$ & $0.016 \pm 0.004$ & 1.00 & $1.7 \pm 0.0$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.0006 \pm 0.0036$ & 2.52 & $1.4 \pm 0.0$ \\  GT-P1000 & $0.0096 \pm 0.0009$ & $0.0000 \pm 0.0061$ & 1.73 & $0.94 \pm 0.02$ \\  GT-I9300 & $0.15 \pm 0.00$ & $0.014 \pm 0.001$ & 6.16 & $0.64 \pm 0.01$ \\  GT-I9505 & $0.0 \pm 0$ & $0.18 \pm 0.00$ & 6.83 & $0.56 \pm 0.01$ \\  GT-N7100 & $0.067 \pm 0.002$ & $0.0011 \pm 0.0058$ & 6.91 & $0.28 \pm 0.02$ \\  HTC Desire HD & $0.0 \pm 0$ & $0.0005 \pm 0.0070$ & 3.05 & $0.27 \pm 0.02$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table}}
\newcommand{\daTabSecScoressummary}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline nexus & $0.36 \pm 0.00$ & $0.52 \pm 0.00$ & 0.68 & $5.0 \pm 0.0$ \\  notnexus & $0.12 \pm 0.00$ & $0.039 \pm 0.000$ & 0.64 & $2.7 \pm 0.0$ \\ \end{tabular} \caption{Security scores for summaries} \label{tab:sec_summary} \end{table}}
\newcommand{\daUpdatednessPerc}{$5.6 \pm 0.0\%$}

@@

\newcommand{\daSecScoreBestmanufacturerScore}{$3.4 \pm 0.0$}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.18 \pm 0.00$}
\newcommand{\daSecScoreBestmodelScore}{$4.8 \pm 0.0$}
\newcommand{\daSecScoreWorstmodelScore}{$0.27 \pm 0.02$}

@@

\newcommand{\daVulnFree}{$0.13 \pm 0.00$}

@@

\newcommand{\daTabSecScoresoperator}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.25 \pm 0.00$ & $0.12 \pm 0.00$ & 0.37 & $3.8 \pm 0.0$ \\  T-Mobile & $0.19 \pm 0.00$ & $0.18 \pm 0.00$ & 0.48 & $3.6 \pm 0.0$ \\  Orange & $0.21 \pm 0.00$ & $0.085 \pm 0.003$ & 0.39 & $3.5 \pm 0.0$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & 0.44 & $3.4 \pm 0.0$ \\  3 & $0.15 \pm 0.00$ & $0.093 \pm 0.003$ & 0.49 & $3.2 \pm 0.0$ \\  AT\&T & $0.12 \pm 0.00$ & $0.077 \pm 0.002$ & 0.43 & $3.1 \pm 0.0$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.10 \pm 0.00$ & 0.52 & $3.1 \pm 0.0$ \\  Verizon & $0.18 \pm 0.00$ & $0.087 \pm 0.002$ & 0.81 & $2.8 \pm 0.0$ \\  unknown & $0.097 \pm 0.001$ & $0.22 \pm 0.00$ & 1.07 & $2.6 \pm 0.0$ \\  n Telenor & $0.026 \pm 0.001$ & $0.10 \pm 0.00$ & 1.42 & $1.6 \pm 0.0$ \\  Airtel & $0.065 \pm 0.002$ & $0.028 \pm 0.002$ & 1.95 & $1.1 \pm 0.0$ \\  Grameenphone & $0.0077 \pm 0.0005$ & $0.015 \pm 0.001$ & 2.03 & $0.77 \pm 0.00$ \\  Robi & $\left(8.0 \pm 8.0\right) \times 10^{-5}$ & $0.040 \pm 0.003$ & 2.22 & $0.71 \pm 0.01$ \\  banglalink & $0.00016 \pm 0.00011$ & $0.029 \pm 0.002$ & 2.92 & $0.39 \pm 0.00$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table}}

@@

\newcommand{\daSecScoreBestoperatorScore}{$3.8 \pm 0.0$}

@@

\newcommand{\daSecScoreWorstoperatorScore}{$0.39 \pm 0.00$}

@@

\newcommand{\daAPICurveFitParamFirst}{110.0}

@@

\newcommand{\daOSCurveHalfDeployed}{$\left(3.1 \pm 0.8\right) \times 10^{2}$}
\newcommand{\daOSCurveFullDeployed}{$\left(0.0 \pm 2.4\right) \times 10^{5}$}

@@

\newcommand{\daAPICurveHalfDeployed}{$\left(3.3 \pm 0.8\right) \times 10^{2}$}
\newcommand{\daAPICurveFullDeployed}{$\left(0.0 \pm 2.4\right) \times 10^{5}$}

@@

\newcommand{\daUpdatesPerYear}{$1.4 \pm 0.0$}

@@

\newcommand{\daMeanInsecurityPercNominal}{87.2\%}

@@

\newcommand{\daUpdatednessPercNominal}{5.61\%}

@@

\newcommand{\daOSCurveHalfDeployedNominal}{308.0}

@@

\newcommand{\daAPICurveHalfDeployedNominal}{330.0}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.394}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.177}

>>>>

\newcommand{\daMeanInsecurityPerc}{$87.2 \pm 0.0342\%$}

@@

\newcommand{\daUpdatedness}{$0.0561 \pm 0.000258$}
\newcommand{\daSecurityScore}{$2.75 \pm 0.00157$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline LG & $0.12 \pm 0.00$ & $0.32 \pm 0.00$ & 0.74 & $3.38 \pm 0.01$ \\  Motorola & $0.16 \pm 0.00$ & $0.13 \pm 0.00$ & 0.77 & $2.94 \pm 0.01$ \\  other & $0.13 \pm 0.00$ & $0.06 \pm 0.00$ & 0.64 & $2.75 \pm 0.00$ \\  Samsung & $0.14 \pm 0.00$ & $0.05 \pm 0.00$ & 0.71 & $2.67 \pm 0.00$ \\  Sony & $0.13 \pm 0.00$ & $0.18 \pm 0.00$ & 1.02 & $2.64 \pm 0.01$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & 0.89 & $2.55 \pm 0.00$ \\  asus & $0.16 \pm 0.00$ & $0.56 \pm 0.01$ & 6.06 & $2.31 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 4.91 & $0.18 \pm 0.00$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table}}
\newcommand{\daTabSecScoresmodel}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.54 \pm 0.00$ & $0.53 \pm 0.01$ & 1.53 & $4.80 \pm 0.03$ \\  Nexus 4 & $0.23 \pm 0.00$ & $0.82 \pm 0.01$ & 6.06 & $3.39 \pm 0.04$ \\  Nexus 7 & $0.19 \pm 0.00$ & $0.74 \pm 0.01$ & 5.92 & $3.02 \pm 0.04$ \\  other & $0.13 \pm 0.00$ & $0.12 \pm 0.00$ & 0.64 & $2.94 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & 0.39 & $2.91 \pm 0.02$ \\  HTC Sensation & $0.36 \pm 0.00$ & $0.01 \pm 0.01$ & 1.59 & $2.47 \pm 0.02$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & 1.20 & $2.33 \pm 0.01$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & 1.00 & $1.75 \pm 0.01$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & 2.52 & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & 1.73 & $0.94 \pm 0.02$ \\  GT-I9300 & $0.15 \pm 0.00$ & $0.01 \pm 0.00$ & 6.17 & $0.64 \pm 0.01$ \\  GT-I9505 & $0.00 \pm 0.00$ & $0.18 \pm 0.00$ & 6.83 & $0.56 \pm 0.01$ \\  GT-N7100 & $0.07 \pm 0.00$ & $0.00 \pm 0.01$ & 6.91 & $0.28 \pm 0.02$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & 3.05 & $0.27 \pm 0.02$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table}}
\newcommand{\daTabSecScoressummary}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline nexus & $0.36 \pm 0.00$ & $0.52 \pm 0.00$ & 0.68 & $5.02 \pm 0.01$ \\  notnexus & $0.12 \pm 0.00$ & $0.04 \pm 0.00$ & 0.64 & $2.68 \pm 0.00$ \\ \end{tabular} \caption{Security scores for summaries} \label{tab:sec_summary} \end{table}}
\newcommand{\daUpdatednessPerc}{$5.61 \pm 0.0258\%$}

@@

\newcommand{\daSecScoreBestmanufacturerScore}{$3.38 \pm 0.011$}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.175 \pm 0.00428$}
\newcommand{\daSecScoreBestmodelScore}{$4.8 \pm 0.0254$}
\newcommand{\daSecScoreWorstmodelScore}{$0.274 \pm 0.0209$}

@@

\newcommand{\daVulnFree}{$0.128 \pm 0.000342$}

@@

\newcommand{\daTabSecScoresoperator}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.25 \pm 0.00$ & $0.12 \pm 0.00$ & 0.37 & $3.79 \pm 0.01$ \\  T-Mobile & $0.19 \pm 0.00$ & $0.18 \pm 0.00$ & 0.48 & $3.57 \pm 0.01$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & 0.39 & $3.52 \pm 0.02$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & 0.44 & $3.41 \pm 0.01$ \\  3 & $0.15 \pm 0.00$ & $0.09 \pm 0.00$ & 0.49 & $3.15 \pm 0.01$ \\  AT\&T & $0.12 \pm 0.00$ & $0.08 \pm 0.00$ & 0.43 & $3.08 \pm 0.01$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.10 \pm 0.00$ & 0.52 & $3.07 \pm 0.01$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & 0.81 & $2.82 \pm 0.01$ \\  unknown & $0.10 \pm 0.00$ & $0.22 \pm 0.00$ & 1.08 & $2.57 \pm 0.01$ \\  n Telenor & $0.03 \pm 0.00$ & $0.10 \pm 0.00$ & 1.42 & $1.58 \pm 0.01$ \\  Airtel & $0.07 \pm 0.00$ & $0.03 \pm 0.00$ & 1.96 & $1.08 \pm 0.01$ \\  Grameenphone & $0.01 \pm 0.00$ & $0.01 \pm 0.00$ & 2.04 & $0.76 \pm 0.00$ \\  Robi & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 2.23 & $0.70 \pm 0.01$ \\  banglalink & $0.00 \pm 0.00$ & $0.03 \pm 0.00$ & 2.95 & $0.39 \pm 0.00$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table}}

@@

\newcommand{\daSecScoreBestoperatorScore}{$3.79 \pm 0.0128$}

@@

\newcommand{\daSecScoreWorstoperatorScore}{$0.386 \pm 0.0049$}

@@

\newcommand{\daAPICurveFitParamFirst}{110}

@@

\newcommand{\daOSCurveHalfDeployed}{$308 \pm 81.8$}
\newcommand{\daOSCurveFullDeployed}{$1\,040 \pm 235\,000$}

@@

\newcommand{\daAPICurveHalfDeployed}{$330 \pm 84.0$}
\newcommand{\daAPICurveFullDeployed}{$1\,060 \pm 236\,000$}

@@

\newcommand{\daUpdatesPerYear}{$1.35 \pm 0.0209$}

@@

\newcommand{\daMeanInsecurityPercNominal}{8\,720\%}

@@

\newcommand{\daUpdatednessPercNominal}{561\%}

@@

\newcommand{\daOSCurveHalfDeployedNominal}{308}

@@

\newcommand{\daAPICurveHalfDeployedNominal}{330}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.386}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.175}

### 2014-11-12 securityupdates.tex
updated data and some figures

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe insecure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered.
This graph is explained further in XXX.}
\label{fig:proportioninsecure}
\end{figure}

@@

It is clear from Figure~\ref{fig:proportioninsecure} that Android devices are often exposed to known security vulnerabilities.
One solution is regulation, and indeed there is ongoing legal action to force network operators to ship updates for security vulnerabilities~\cite{Soghoian2013}.\todolater{Check on the status of this legal action}
Indeed, many smartphones are sold on 12--24 month contracts, and yet our data shows many devices do not receive many security updates. 
In contrast, Windows XP could be purchased for a one-off payment in October 2001 and received security updates until April 2014.

@@

\begin{figure}
 \includegraphics[width=\columnwidth]{figures/nvulnerabilities_heat.pdf}
 \caption{Proportion of devices affected by different vulnerabilities}
 \label{fig:nvulnerabilities_heat}
\end{figure}

@@

\subsubsection{Results}
\begin{figure}
 \centering
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/device-data-all-security}
  \caption{Number of vulnerabilities affecting each device over time}
  \label{fig:device_data_security}
 \end{subfigure}
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/device-data-all-os}
  \caption{OS versions over time. Black vertical lines indicate that the build number changed without changing the OS version at that point.}
  \label{fig:device_data_os}
 \end{subfigure}
 \caption{The top \daNumDeviceDataDevices\ devices by days of contribution in the \da\ data. One strip per device.}
\end{figure}
The longitudinal data on the number of vulnerabilities affecting the \daNumDeviceDataDevices\ devices which have contributed the most days of data to \da\ changes over time is shown in Figure~\ref{fig:device_data_security}.
The trend that we saw in Figure~\ref{fig:proportioninsecure} of security improving and then getting worse is also shown here.
It shows how some devices had vulnerabilities, which were fixed, and then further vulnerabilities were discovered, and for these devices, mostly not fixed.
This implies that these devices had been abandoned by the device manufacturer and were not receiving updates which is confirmed by Figure~\ref{fig:device_data_os} which shows which OS versions those devices were running.
Some devices start off in 2011 exposed to known security vulnerabilities and are still exposed to those and additional ones in 2014.

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe insecure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered with those which have the biggest impact annotated.
This graph is explained further in XXX.}
\label{fig:proportioninsecure}
\end{figure}

@@

It is clear from Figure~\ref{fig:proportioninsecure} that Android devices are often exposed to known security vulnerabilities.
One solution is regulation, and indeed there is ongoing legal action to force network operators to ship updates for security vulnerabilities~\cite{Soghoian2013}.\todolater{Check on the status of this legal action}
Indeed, many smartphones are sold on 12--24 month contracts, and yet our data shows many devices do not receive many security updates (\daUpdatesPerYear\ per year). 
In contrast, Windows XP could be purchased for a one-off payment in October 2001 and received security updates until April 2014.

@@

\begin{figure*}
 \includegraphics[width=\textwidth]{figures/nvulnerabilities_heat.pdf}
 \caption{Proportion of devices affected by different vulnerabilities. The prefix `m-' indicates `maybe insecure' and `d-' indicates `definitely insecure'. The first few vulnerabilities are all `maybe insecure' as we do not have data from before that vulnerability was discovered while later ones are mostly `definitely insecure' as we know no fixing update reached the devices.}
 \label{fig:nvulnerabilities_heat}
\end{figure*}

@@

\subsubsection{Results}
\begin{figure}
 \centering
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/device-data-all-os}
  \caption{OS versions over time. Black vertical lines indicate that the build number changed without changing the OS version at that point.}
  \label{fig:device_data_os}
 \end{subfigure}
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/device-data-all-security}
  \caption{Number of vulnerabilities affecting each device over time}
  \label{fig:device_data_security}
 \end{subfigure}
 \caption{The top \daNumDeviceDataDevices\ devices by days of contribution in the \da\ data. One strip per device.}
\end{figure}
The longitudinal data on the number of vulnerabilities affecting the \daNumDeviceDataDevices\ devices which have contributed the most days of data to \da\ changes over time is shown in Figure~\ref{fig:device_data_security}.
The trend that we saw in Figure~\ref{fig:proportioninsecure} of security improving and then getting worse is also shown here.
It shows how some devices had vulnerabilities, which were fixed, and then further vulnerabilities were discovered, and for these devices, mostly not fixed.
This implies that these devices had been abandoned by the device manufacturer and were not receiving updates which is confirmed by Figure~\ref{fig:device_data_os} which shows which OS versions those devices were running.
Some devices start off in 2011 exposed to known security vulnerabilities and are still exposed to those and additional ones in 2014.
